---
title: "End of Year MyEmma"
author: "Kate Spiekerman, kls5665"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r global_options, echo=FALSE}
knitr::opts_chunk$set(fig.height=4, fig.width=5, warning=FALSE, tidy=TRUE, tidy.opts=list(width.cutoff=60))
```


```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(ggplot2)
```

```{r, echo=FALSE}
my_emma <- read.csv('my_emma.csv')

opens <- my_emma %>%
  filter(Action == 'opens')

austin <- my_emma %>%
  filter(Action == 'sent to' & Area == 'Austin')

four_points <- my_emma %>%
  filter(Action == 'sent to' & Area == 'Four Points')

lake_travis <- my_emma %>%
  filter(Action == 'Sent to' & Area == 'Lake Travis')

cedar_park <- my_emma %>%
  filter(Action == 'sent to' & Area == 'Cedar Park')

round_rock <- my_emma %>%
  filter(Action == 'sent to' & Area == 'Round Rock')

westlake <- my_emma %>%
  filter(Action == 'sent to' & Area == 'Westlake')

44091 / (5000 * 6 + 2755 * 3 + 690 * 6 + 1833 * 2 + 701 * 6 + 4306 * 6) * 100

```

**Number of Area that Used Each Email**

Pre giving- 5

Giving- 5

Post Giving- 4

Merry Christmas- 5

Last Chance- 5

Happy New Year- 5

**Number of Emails Each Area Used**

Austin- 6

Four Points- 3

Lake Travis- 6

Cedar Park- 2

Round Rock- 6

Westlake- 6

**Sent to By Area**

Austin- 5000

Four Points- 2755

Lake Travis- 690

Cedar Park- 1833

Round Rock- 701

Westlake- 4306



**Overall Open Rate:**
57.93%

```{r, echo=FALSE, message=FALSE}
pre_giving_opens <- opens %>%
  filter(Email.Title == 'Pre-Giving Tuesday')

7732 / (5000 + 690 + 1833 + 701 + 4306) * 100

giving_opens <- opens %>%
  filter(Email.Title == 'Giving Tuesday')

7113 / (5000 + 690 + 1833 + 701 + 4306) * 100

post_giving_opens <- opens %>%
  filter(Email.Title == 'Post Giving Tuesday')

7732 / (5000 + 690 + 701 + 4306) * 100

merry_christmas_opens <- opens %>%
  filter(Email.Title == 'Merry Christmas')

7806 / (5000 + 690 + 701 + 4306 + 2755) * 100

last_chance_opens <- opens %>%
  filter(Email.Title == 'Last Chance' | Email.Title == 'Last Chance EOY')

7492 / (5000 + 690 + 701 + 4306 + 2755) * 100

happy_new_years_opens <- opens %>%
  filter(Email.Title == 'Happy New Year' | Email.Title == 'Post New Years' | Email.Title == 'Happy New Years')

7535 / (5000 + 690 + 701 + 4306 + 2755) * 100

```


**Opens Rates by Email**

Pre-Giving: 61.71%

Giving: 56.77%

Post-Giving: 72.28%

Merry Christmas: 58.03%

Last Chance: 55.69%

Happy New Year: 56.01%

```{r, echo=FALSE, message=FALSE}
1868 / (5000 * 6 + 2755 * 3 + 690 * 6 + 1833 * 2 + 701 * 6 + 4306 * 6) * 100
```


**Overall Click Rate:**
2.45%


```{r, echo=FALSE, message=FALSE}
clicks <- my_emma %>%
  filter(Action == 'clicks')

pre_giving_clicks <- clicks %>%
  filter(Email.Title == 'Pre-Giving Tuesday')

318 / (5000 + 690 + 1833 + 701 + 4306) * 100

giving_clicks <- clicks %>%
  filter(Email.Title == 'Giving Tuesday')

382 / (5000 + 690 + 1833 + 701 + 4306) * 100

post_giving_clicks <- clicks %>%
  filter(Email.Title == 'Post Giving Tuesday')

498 / (5000 + 690 + 701 + 4306) * 100

merry_christmas_clicks <- clicks %>%
  filter(Email.Title == 'Merry Christmas')

125 / (5000 + 690 + 701 + 4306 + 2755) * 100

last_chance_clicks <- clicks %>%
  filter(Email.Title == 'Last Chance' | Email.Title == 'Last Chance EOY')

257 / (5000 + 690 + 701 + 4306 + 2755) * 100

happy_new_years_clicks <- clicks %>%
  filter(Email.Title == 'Happy New Year' | Email.Title == 'Post New Years' | Email.Title == 'Happy New Years')

256 / (5000 + 690 + 701 + 4306 + 2755) * 100
```


**Click Rates by Email**

Pre-Giving: 2.54%

Giving: 3.05%

Post-Giving: 4.66%

Merry Christmas: .93%

Last Chance: 1.91%

Happy New Year: 1.90%


```{r, echo=FALSE, message=FALSE}
781 / (5000 * 6 + 2755 * 3 + 690 * 6 + 1833 * 2 + 701 * 6 + 4306 * 6) * 100
```


**Overall Optout Rate:**
1.03%


```{r, echo=FALSE, message=FALSE}
optouts <- my_emma %>%
  filter(Action == 'optout' | Action == 'optouts')

pre_giving_opt <- optouts %>%
  filter(Email.Title == 'Pre-Giving Tuesday')

158 / (5000 + 690 + 1833 + 701 + 4306) * 100

giving_opt <- optouts %>%
  filter(Email.Title == 'Giving Tuesday')

141 / (5000 + 690 + 1833 + 701 + 4306) * 100

post_giving_opt <- optouts %>%
  filter(Email.Title == 'Post Giving Tuesday')

41 / (5000 + 690 + 701 + 4306) * 100

merry_christmas_opt <- optouts %>%
  filter(Email.Title == 'Merry Christmas')

121 / (5000 + 690 + 701 + 4306 + 2755) * 100

last_chance_opt <- optouts %>%
  filter(Email.Title == 'Last Chance' | Email.Title == 'Last Chance EOY')

135 / (5000 + 690 + 701 + 4306 + 2755) * 100

happy_new_years_opt <- optouts %>%
  filter(Email.Title == 'Happy New Year' | Email.Title == 'Post New Years' | Email.Title == 'Happy New Years')

130 / (5000 + 690 + 701 + 4306 + 2755) * 100
```


**Click Rates by Email**

Pre-Giving: 1.26%

Giving: 1.13%

Post-Giving: .38%

Merry Christmas: .90%

Last Chance: 1.00%

Happy New Year: .97%

```{r, echo=FALSE}
austin_open <- opens %>%
  filter(Area == 'Austin')

17273 / (5000 * 6) * 100

four_points_open <- opens %>%
  filter(Area == 'Four Points')

4545 / (2755 * 3) * 100

lake_travis_open <- opens %>%
  filter(Area == 'Lake Travis')

2668 / (690 * 6) * 100

cedar_park_open <- opens %>%
  filter(Area == 'Cedar Park')

2108 / (1833 * 2) * 100

round_rock_open <- opens %>%
  filter(Area == 'Round Rock')

2479 / (701 * 6) * 100

westlake_open <- opens %>%
  filter(Area == 'Westlake')

15018 / (4306 * 6) * 100
```

**Area Average Open Rate**

Austin- 57.58%

Four Points- 54.99%

Lake Travis- 64.44%

Cedar Park- 57.50%

Round Rock- 58.94%

Westlake- 58.13%


```{r, echo=FALSE}
austin_click <- clicks %>%
  filter(Area == 'Austin')

137 / (5000 * 6) * 100

four_points_click <- clicks %>%
  filter(Area == 'Four Points')

96 / (2755 * 3) * 100

lake_travis_click <- clicks %>%
  filter(Area == 'Lake Travis')

69 / (690 * 6) * 100

cedar_park_click <- clicks %>%
  filter(Area == 'Cedar Park')

45 / (1833 * 2) * 100

round_rock_click <- clicks %>%
  filter(Area == 'Round Rock')

34 / (701 * 6) * 100

westlake_click <- clicks %>%
  filter(Area == 'Westlake')

1487 / (4306 * 6) * 100
```


**Area Average Click Rate**

Austin- .46%

Four Points- 1.16%

Lake Travis- 1.67%

Cedar Park- 1.23%

Round Rock- .81%

Westlake- 5.76%


```{r, echo=FALSE}
austin_opt <- optouts %>%
  filter(Area == 'Austin')

347 / (5000 * 6) * 100

four_points_opt <- optouts %>%
  filter(Area == 'Four Points')

121 / (2755 * 3) * 100

lake_travis_opt <- optouts %>%
  filter(Area == 'Lake Travis')

10 / (690 * 6) * 100

cedar_park_opt <- optouts %>%
  filter(Area == 'Cedar Park')

33 / (1833 * 2) * 100

round_rock_opt <- optouts %>%
  filter(Area == 'Round Rock')

44 / (701 * 6) * 100

westlake_opt <- optouts %>%
  filter(Area == 'Westlake')

226 / (4306 * 6) * 100
```

**Area Average Unsubscribe Rate**

Austin- 1.16%

Four Points- 1.46%

Lake Travis- .24%

Cedar Park- .90%

Round Rock- 1.05%%

Westlake- .87%


**Number of Emails Opened prior to Giving**

Pre-giving Opens: 7732







